### 2023-09-03 sections/3-datasets.tex
move benchmarking specs

\section{Datasets}
\label{sec:datasets-and-distance-functions}

@@

We benchmark on a variety of datasets from the ann-benchmarks suite~\cite{Aumller2018ANNBenchmarksAB}, 
listed below, along with the appropriate distance function.
Table~\ref{table:datasets:summary} summarizes the properties of these datasets.

>>>>

\section{Datasets And Benchmarking}
\label{sec:datasets-and-distance-functions}

@@

We benchmark on a variety of datasets from the ann-benchmarks suite~\cite{Aumller2018ANNBenchmarksAB}, 
along with the appropriate distance function.
Table~\ref{table:datasets:summary} summarizes the properties of these datasets.

Our systems used for benchmarking were as follows:

\emph{(I don't think we have any macbook benchmarks, right?)}

Ark: 28-core Intel Xeon E5-2690 v4 2.60GHz, 512GB RAM, Manjaro Linux with kernel 5.15.78-1-MANJARO \#1 SMP PREEMPT. Rust 1.70, Python 3.10.5

Macbook Air: 8-core (4 performance, 4 efficiency) Apple M1 processor with 16GB RAM, macOS 12.1. Rust 1.70, Python 3.9.4

Amazon AWS: 64-core Intel Xeon Platinum 8375C CPU 2.90GHz, 512GB RAM, Ubuntu 22.04.3-Ubuntu SMP. Rust 1.71.1, Python 3.10.12
